## IDENTIFICATION OF CANDIDATE MANAGEMENT PROCEDURES  {#sec:mp}

@anderson2020gfmp screened all MPs available in DLMtool as of November 2019. DLMtool includes data-limited MPs that make different types of management recommendations, including adjustments to total allowable catch (TAC), effort, or spatial allocation of catch or effort.
This represents a fairly comprehensive set of data-limited MPs available in the primary literature or agency reports to date.
@anderson2020gfmp also adjusted some of the DLMtool MPs to accommodate the types of data available for BC groundfish (e.g., biennial surveys in several management areas), or to reflect fishery operations.
The MP Framework only considers MPs that make TAC recommendations, because most groundfish stocks are managed by quotas and TACs.

The MP Framework focuses on two main types of MPs: empirical (data-based) and model-based MPs.
@anderson2020gfmp excluded certain MPs from the MP Framework based on a number
of requirements that would rarely be met for BC groundfish stocks. Excluded MPs were those that required: knowledge of absolute abundance; recent age-composition data;  knowledge of depletion; and knowledge of steepness (*h*) of the stock-recruit relationship, since these are likely to be major axes of uncertainty for the stocks to which this framework will be applied.
While it is necessary to explore these axes of uncertainty within OMs, implementing MPs real data that require knowledge of these factors would require many additional assumptions.

A library of all MPs considered in the MP Framework is provided in @anderson2020gfmp (their Appendix D). MPs considered for this Inside Yelloweye Rockfish rebuilding plan are framework are detailed here in Appendix \@ref(app:MPs). 

All MPs included in this framework are described in Appendix \@ref(app:mps).

### CANDIDATE MPs {#sec:approach4-candidate-mps}

We started with the full set of provisional candidate MPs described in Section TODO (Table \@ref(tab:mps)).



```{r mps, results='asis'}
mp <- readr::read_csv(here("mse",  "mp.txt"), comment = "#")
csasdown::csas_table(mp, caption = "Candidate MPs.", col_names = c("Management procedure", "MP type"))
```






```{r mps, results='asis'}
mp <- readr::read_csv(here("mse",  "mp.txt"), comment = "#")
csasdown::csas_table(mp, caption = "Candidate MPs.", col_names = c("Management procedure", "MP type"))
```

## Reference MPs
<!-- Only No fishing (NFref), FMSY75 and FMSY -->



## Fixed TAC MPs

- Look at different values of fixed catch, including 5, 10, and 15 t. 15 t can be considered the status quo.

## Index-based MPs

Index-based MPs set the TAC relative to the change in the index over time. Slope-based MPs increase or decrease the TAC in accordance with the estimated slope in the index over recent time, while ratio MPs increase or decrease the TAC in accordance with the ratio of the index from two different time periods.

A third type, target MPs, adjusts the TAC based on the ratio of the recent index and a target index value. These were not considered here as further guidance from management would be needed in order to select the appropriate target value. For the rebuilding plan, the goal is to ensure that the stock is above the LRP, however, the LRP is not likely to be the target state of nature that would be suitable for management and stakeholders.

Evaluate index MPs with either annual or 5-year updates. For the latter, fixed TAC between updates.

All index-based MPs set a minimum TAC = 0.5 t for surveys.

### Index slope

$\text{TAC}_y = C_{y-1} (1 + \lambda I^{\text{slope}}_{y-1})$

<!-- Geromont, H.F. and Butterworth, D.S. 2014. Complex assessment or simple management procedures for efficient fisheries management: a comparative study. ICES J. Mar. Sci. doi:10.1093/icesjms/fsu017 -->

Various tuning parameters can alter performance of MPs:
Lambda controls the change in TAC relative to change in slope.
I_slope can vary by the number of years in which the slope is calculated.
Two types of index slope MPs:

GB_slope - use above eq but ensure that $0.8 C_{y-1} \le TAC_y \le 1.2 C_{y-1}$.

Three configurations to explore:
GB_slope_lambda1   $\lambda = 1$	  $I^{slope}_{y-1}$ is calculated from index in the preceding 5 years
GB_slope_lambda05  $\lambda = 0.5$	$I^{slope}_{y-1}$ is calculated from the preceding 5 years
GB_slope_yrs10     $\lambda = 1$	  $I^{slope}_{y-1}$ is calculated from the preceding 10 years


Islope - no cap. Thus smaller values of $\lambda$ may be prudent.

Islope_5_lambda04  $\lambda = 0.4$	  $I^{slope}_{y-1}$ is calculated from index in the preceding 5 years
Islope_10_lambda04 $\lambda = 0.4$	$I^{slope}_{y-1}$ is calculated from the preceding 10 years
Islope_10_lambda08 $\lambda = 0.8$	  $I^{slope}_{y-1}$ is calculated from the preceding 10 years


### Index ratio

$\text{TAC}_y = C_{y-1} \dfrac{I^{\text{recent}}}{I^{\text{historical}}}$

<!-- Ernesto Jardim, Manuela Azevedo, Nuno M. Brites, Harvest control rules for data limited stocks using length-based reference points and survey biomass indices, Fisheries Research, Volume 171, November 2015, Pages 12-19, ISSN 0165-7836, https://doi.org/10.1016/j.fishres.2014.11.013 -->


$I^{\text{recent}}$ is the mean index from the most recent years, $I^{\text{historical}}$ is the mean from years preceding that for $I^{\text{recent}}$.
The number of years for $I^{\text{recent}}$ and $I^{\text{historical}}$ can vary. Two options were explored:

Iratio_23  $I^{\text{recent}}$ is from the preceding 2 years, e.g., 2018-2019
           $I^{\text{historical}}$ is from the 3 years preceding $I^{\text{recent}}$, e.g., 2015-2017

Iratio_55  $I^{\text{recent}}$ is from the preceding 5 years, e.g., 2015-2019
           $I^{\text{historical}}$ is from the 5 years preceding $I^{\text{recent}}$, e.g., 2010-2014

### IDX

<!-- Cox et al. Res Doc in press -->


## SP MPs
- State-space surplus production model (should be documented in gfmp appendix?) with prior for intrinsic rate of increase from 2011 assessment.
- Two ramped harvest control rules:
a. 80-40% BMSY as the USR, LRP
b. 40-10% B0 as the USR, LRP
- Two assessment frequencies (5 and 10 years)
- Fixed TAC between assessments

#### Reference MPs

In addition to the candidate MPs, it is important to include reference MPs. Provisionally, we suggest the following reference MPs:

* No fishing
* Fishing at F/F~MSY~
* Fishing at 0.75 F/F~MSY~
* Maintaining the current TAC

The purpose of reference MPs is not to explore viable management strategies but to bound the range of expected or possible performance and contextualize whether differences between performance statistics among MPs are meaningful [@punt2016]. For example, the "no fishing" reference MPs provides information on maximum possible stock levels and the maximum possible rate of rebuilding under a rebuilding scenario. The "fishing at 0.75 F/F~MSY~" MP illustrates performance under an omniscient manager with perfect information. The MP that maintains the current TAC is included not because we think it is necessarily a good management strategy but illustrates what is likely the default had the framework not been implemented and illustrates the long-term performance expectations given current exploitation levels.

## STEP 4: IDENTIFICATION OF CANDIDATE MANAGEMENT PROCEDURES  {#sec:results4}


