\newpage

`r if(knitr:::is_latex_output()) '\\Appendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

```{r message = FALSE}
library(MSEtool)
knitr_results <- TRUE
knitr_echo <- TRUE
```

# INSIDE YELLOWEYE ROCKFISH OPERATING MODEL DEFINITION {#app:desc-om-yelloweye}

## STOCK SLOT DESCRIPTIONS {#app:desc-stock-yelloweye}

```{r warnings = FALSE}
stock_yelloweye <- methods::new("Stock")
stock_yelloweye@Name <- "Inside Yelloweye Rockfish"
```

<!-- slot-chunk-begin -->
### Common_Name {#app:desc-stock-common_name-yelloweye}

*Common name of the species.*

```{r desc-stock-common_name-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Common_Name <- "Yelloweye Rockfish"
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Species {#app:desc-stock-species-yelloweye}

*Scientific name of the species.*

```{r desc-stock-species-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Species <- "Sebastes ruberrimus"
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### maxage {#app:desc-stock-maxage-yelloweye}

*The maximum age of individuals that is simulated. Positive integer.*

```{r desc-stock-maxage-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@maxage <- 80
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### M {#app:desc-stock-m-yelloweye}

*Natural mortality rate. Uniform distribution lower and upper bounds.*

```{r desc-stock-m-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@M
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### h {#app:desc-stock-h-yelloweye}

*Steepness of the stock_yelloweye-recruit relationship. Uniform distribution lower and upper bounds with values from 1/5 to 1.*

```{r desc-stock-h-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@h
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### SRrel {#app:desc-stock-srrel-yelloweye}

*Type of stock_yelloweye-recruit relationship. Single integer value, switch (1) Beverton-Holt (2) Ricker.*

```{r desc-stock-srrel-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@SRrel <- 1
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Perr {#app:desc-stock-perr-yelloweye}

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds.*

```{r desc-stock-perr-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Perr
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Linf {#app:desc-stock-linf-yelloweye}

*Maximum length. Uniform distribution lower and upper bounds.*

```{r desc-stock-linf-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Linf
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### K {#app:desc-stock-k-yelloweye}

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds.*

```{r desc-stock-k-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@K
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### t0 {#app:desc-stock-t0-yelloweye}

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds.*

```{r desc-stock-t0-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@t0
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### L50 {#app:desc-stock-l50-yelloweye}

*Length at 50% maturity. Uniform distribution lower and upper bounds.*

```{r desc-stock-l50-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@L50
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### L50_95 {#app:desc-stock-l50_95-yelloweye}

*Length increment from 50% to 95% maturity. Uniform distribution lower and upper bounds.*

```{r desc-stock-l50_95-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@L50_95
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### a {#app:desc-stock-a-yelloweye}

*Length-weight parameter alpha. Positive real number.*

```{r desc-stock-a-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@a
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### b {#app:desc-stock-b-yelloweye}

*Length-weight parameter beta. Positive real number.*

```{r desc-stock-b-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@b
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Fdisc {#app:desc-stock-fdisc-yelloweye}

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds.*

Not used, we assume all sources of mortality are included in catch.

```{r desc-stock-fdisc-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Fdisc <- c(1, 1)
```
<!-- slot-chunk-end -->

## FLEET SLOT DESCRIPTIONS {#app:desc-fleet-yelloweye}

```{r warnings = FALSE}
fleet_yelloweye <- DLMtool::Generic_Fleet
```

<!-- slot-chunk-begin -->
### Name {#app:desc-fleet-name-yelloweye}

*Name of the Fleet object.*

```{r desc-fleet-name-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@Name
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### nyears {#app:desc-fleet-nyears-yelloweye}

*The number of years for the historical spool-up simulation.*

```{r desc-fleet-nyears-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@nyears
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### L5 {#app:desc-fleet-l5-yelloweye}

*Shortest length corresponding to 5% vulnerability. Uniform distribution lower and upper bounds.*

Selectivity of recreational and commercial fleets are fixed in SRA_scope, which updates the OM.

TODO: give here and plot?

```{r desc-fleet-l5-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@L5
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### LFS {#app:desc-fleet-lfs-yelloweye}

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds.*

TODO: give here and plot?

Selectivity of recreational and commercial fleets are fixed in SRA_scope, which updates the OM.

```{r desc-fleet-lfs-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@LFS
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Vmaxlen {#app:desc-fleet-vmaxlen-yelloweye}

*The vulnerability of fish at `Linf`. Uniform distribution lower and upper bounds. Fraction.*

Selectivity of recreational and commercial fleets are fixed in SRA_scope, which updates the OM.

```{r desc-fleet-vmaxlen-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@Vmaxlen
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### isRel {#app:desc-fleet-isrel-yelloweye}

<!-- slot-chunk-begin -->
### LR5 {#app:desc-fleet-lr5-yelloweye}

*Shortest length corresponding ot 5% retention. Uniform distribution lower and upper bounds.*

```{r desc-fleet-lr5-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@LR5
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### LFR {#app:desc-fleet-lfr-yelloweye}

*Shortest length that is fully retained. Uniform distribution lower and upper bounds.*

No discard dynamics are modeled. We assume all mortality is accounted for in catch.

```{r desc-fleet-lfr-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@LFR
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Rmaxlen {#app:desc-fleet-rmaxlen-yelloweye}

*The retention of fish at `Linf`. Uniform distribution lower and upper bounds.*

```{r desc-fleet-rmaxlen-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@Rmaxlen
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### DR {#app:desc-fleet-dr-yelloweye}

*Discard rate: the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction.*

No discard dynamics are modeled. We assume all mortality is accounted for in catch.

```{r desc-fleet-dr-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@DR
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### CurrentYr {#app:desc-fleet-currentyr-yelloweye}

*The current calendar year (final year) of the historical simulations (e.g., 2019).*

```{r desc-fleet-currentyr-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@CurrentYr
```
<!-- slot-chunk-end -->

## OBS SLOT DESCRIPTIONS {#app:desc-obs-yelloweye}

```{r warnings = FALSE}
obs_yelloweye <- DLMtool::Precise_Unbiased
```

<!-- slot-chunk-begin -->
### Cobs_yelloweye {#app:desc-obs_yelloweye-cobs_yelloweye-yelloweye}

*Log-normal catch obs_yelloweye observation error expressed as a CV. Uniform distribution lower and upper bounds.*

```{r desc-obs_yelloweye-cobs_yelloweye-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Cobs
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Cbiascv {#app:desc-obs-cbiascv-yelloweye}

*Log-normal CV controlling the sampling of bias in catch obs_yelloweyeervations for each simulation. Uniform distribution lower and upper bounds.*

```{r desc-obs-cbiascv-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Cbiascv
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Iobs_yelloweye {#app:desc-obs_yelloweye-iobs_yelloweye-yelloweye}

*Observation error in the relative abundance indices expressed as a CV. Uniform distribution lower and upper bounds.*

```{r desc-obs_yelloweye-iobs_yelloweye-yelloweye, results = knitr_results, echo = knitr_echo}
#obs_yelloweye@Iobs
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### beta {#app:desc-obs-beta-yelloweye}

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases more slowly than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds.*

```{r desc-obs-beta-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@beta
```
<!-- slot-chunk-end -->

## IMP SLOT DESCRIPTIONS {#app:desc-imp-yelloweye}

```{r warnings = FALSE}
imp_yelloweye <- DLMtool::Perfect_Imp
```

<!-- slot-chunk-begin -->
### Name {#app:desc-imp-name-yelloweye}

*The name of the Implementation error object.*

```{r desc-imp-name-yelloweye, results = knitr_results, echo = knitr_echo}
imp_yelloweye@Name
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### TACFrac {#app:desc-imp-tacfrac-yelloweye}

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds.*

```{r desc-imp-tacfrac-yelloweye, results = knitr_results, echo = knitr_echo}
imp_yelloweye@TACFrac
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### TACSD {#app:desc-imp-tacsd-yelloweye}

*Log-normal CV in the fraction of TAC taken. Uniform distribution lower and upper bounds.*

```{r desc-imp-tacsd-yelloweye, results = knitr_results, echo = knitr_echo}
imp_yelloweye@TACSD
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Maturity {#app:desc-cpars-maturity-yelloweye}

<!-- *To incorporate uncertainty in natural mortality among simulations, we sample from a lognormal distribution using the Hoenig (1983) prior.* -->

<!-- FIXME. What seed? Does the seed get set here? Finish rlnorm eq. This is supposed to be maturity not mortality and why being pulled from cpars?

```{r desc-cpars-maturity-yelloweye, results = knitr_results, echo = knitr_echo}
set.seed(1)
OM_yelloweye@cpars$M <- rlnorm(OM_yelloweye@nsim, )
```


### Natural mortality {#app:desc-cpars-M-yelloweye}

*To incorporate uncertainty in natural mortality among simulations, we sample from a lognormal distribution using the Hoenig (1983) prior.*

```{r desc-cpars-M-yelloweye, results = knitr_results, echo = knitr_echo}
set.seed(1)
OM_yelloweye@cpars$M <- rlnorm(OM_yelloweye@nsim, )
fleet_yelloweye@Name
```
-->

<!-- slot-chunk-end -->

# CONDITIONING THE OPERATING MODEL TO DATA

*TODO: ADD sra section or appendix?*

