```{r message = FALSE}
library(DLMtool)
knitr_results <- TRUE
knitr_echo <- TRUE
```

## STOCK SLOT DESCRIPTIONS {#app:desc-stock-yelloweye}

```{r warnings = FALSE}
stock_yelloweye <- methods::new("Stock")
```

<!-- slot-chunk-begin -->
### Name {#app:desc-stock-name-yelloweye}

*The name of the Stock object.*

```{r desc-stock-name-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Name <- "Inside Yelloweye Rockfish"
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Common_Name {#app:desc-stock-common_name-yelloweye}

*Common name of the species.*

```{r desc-stock-common_name-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Common_Name <- "Yelloweye Rockfish"
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Species {#app:desc-stock-species-yelloweye}

*Scientific name of the species.*

```{r desc-stock-species-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Species <- "Sebastes ruberrimus"
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### maxage {#app:desc-stock-maxage-yelloweye}

*The maximum age of individuals that is simulated. Positive integer.*

```{r desc-stock-maxage-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@maxage
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### R0 {#app:desc-stock-r0-yelloweye}

*The magnitude of unfished recruitment. An arbitrary value that scales all results. Set to 1000.*

```{r desc-stock-r0-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@R0
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### M {#app:desc-stock-m-yelloweye}

*Natural mortality rate. Uniform distribution lower and upper bounds.*

```{r desc-stock-m-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@M
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### h {#app:desc-stock-h-yelloweye}

*Steepness of the stock_yelloweye-recruit relationship. Uniform distribution lower and upper bounds with values from 1/5 to 1.*

```{r desc-stock-h-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@h
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### SRrel {#app:desc-stock-srrel-yelloweye}

*Type of stock_yelloweye-recruit relationship. Single integer value, switch (1) Beverton-Holt (2) Ricker.*

```{r desc-stock-srrel-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@SRrel
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Perr {#app:desc-stock-perr-yelloweye}

*Process error, the CV of lognormal recruitment deviations. Uniform distribution lower and upper bounds.*

```{r desc-stock-perr-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Perr
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### AC {#app:desc-stock-ac-yelloweye}

*Autocorrelation in recruitment deviations. Uniform distribution lower and upper bounds.*

```{r desc-stock-ac-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@AC
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Linf {#app:desc-stock-linf-yelloweye}

*Maximum length. Uniform distribution lower and upper bounds.*

```{r desc-stock-linf-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Linf
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### K {#app:desc-stock-k-yelloweye}

*von Bertalanffy growth parameter k. Uniform distribution lower and upper bounds.*

```{r desc-stock-k-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@K
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### t0 {#app:desc-stock-t0-yelloweye}

*von Bertalanffy theoretical age at length zero. Uniform distribution lower and upper bounds.*

```{r desc-stock-t0-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@t0
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### LenCV {#app:desc-stock-lencv-yelloweye}

*CV of length-at-age (assumed constant for all age classes). Uniform distribution lower and upper bounds.*

```{r desc-stock-lencv-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@LenCV
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### L50 {#app:desc-stock-l50-yelloweye}

*Length at 50% maturity. Uniform distribution lower and upper bounds.*

```{r desc-stock-l50-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@L50
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### L50_95 {#app:desc-stock-l50_95-yelloweye}

*Length increment from 50% to 95% maturity. Uniform distribution lower and upper bounds.*

```{r desc-stock-l50_95-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@L50_95
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### D {#app:desc-stock-d-yelloweye}

*Current level of stock_yelloweye depletion SSB~current~/SSB~unfished~. Uniform distribution lower and upper bounds representing a fraction.*

```{r desc-stock-d-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@D
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### a {#app:desc-stock-a-yelloweye}

*Length-weight parameter alpha. Positive real number.*

```{r desc-stock-a-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@a
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### b {#app:desc-stock-b-yelloweye}

*Length-weight parameter beta. Positive real number.*

```{r desc-stock-b-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@b
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Fdisc {#app:desc-stock-fdisc-yelloweye}

*Fraction of discarded fish that die. Uniform distribution lower and upper bounds.*

```{r desc-stock-fdisc-yelloweye, results = knitr_results, echo = knitr_echo}
stock_yelloweye@Fdisc
```
<!-- slot-chunk-end -->

## FLEET SLOT DESCRIPTIONS {#app:desc-fleet-yelloweye}

```{r warnings = FALSE}
fleet_yelloweye <- DLMtool::Generic_Fleet
```

<!-- slot-chunk-begin -->
### Name {#app:desc-fleet-name-yelloweye}

*Name of the Fleet object.*

```{r desc-fleet-name-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@Name
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### nyears {#app:desc-fleet-nyears-yelloweye}

*The number of years for the historical spool-up simulation.*

```{r desc-fleet-nyears-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@nyears
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Spat_targ {#app:desc-fleet-spat_targ-yelloweye}

*Distribution of fishing in relation to spatial biomass: fishing distribution is proportional to B^`Spat_targ`^. Uniform distribution lower and upper bounds.*

```{r desc-fleet-spat_targ-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@Spat_targ
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### L5 {#app:desc-fleet-l5-yelloweye}

*Shortest length corresponding to 5% vulnerability. Uniform distribution lower and upper bounds.*

```{r desc-fleet-l5-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@L5
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### LFS {#app:desc-fleet-lfs-yelloweye}

*Shortest length that is fully vulnerable to fishing. Uniform distribution lower and upper bounds.*

```{r desc-fleet-lfs-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@LFS
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Vmaxlen {#app:desc-fleet-vmaxlen-yelloweye}

*The vulnerability of fish at `Linf`. Uniform distribution lower and upper bounds. Fraction.*

```{r desc-fleet-vmaxlen-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@Vmaxlen
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### isRel {#app:desc-fleet-isrel-yelloweye}

*Are the selectivity parameters in units of size-of-maturity (`TRUE`) (or absolute units, for example, cm) (`FALSE`).*

```{r desc-fleet-isrel-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@isRel
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### LR5 {#app:desc-fleet-lr5-yelloweye}

*Shortest length corresponding ot 5% retention. Uniform distribution lower and upper bounds.*

```{r desc-fleet-lr5-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@LR5
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### LFR {#app:desc-fleet-lfr-yelloweye}

*Shortest length that is fully retained. Uniform distribution lower and upper bounds.*

```{r desc-fleet-lfr-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@LFR
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Rmaxlen {#app:desc-fleet-rmaxlen-yelloweye}

*The retention of fish at `Linf`. Uniform distribution lower and upper bounds.*

```{r desc-fleet-rmaxlen-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@Rmaxlen
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### DR {#app:desc-fleet-dr-yelloweye}

*Discard rate: the fraction of caught fish that are discarded. Uniform distribution lower and upper bounds. Fraction.*

```{r desc-fleet-dr-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@DR
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### CurrentYr {#app:desc-fleet-currentyr-yelloweye}

*The current calendar year (final year) of the historical simulations (e.g., 2019).*

```{r desc-fleet-currentyr-yelloweye, results = knitr_results, echo = knitr_echo}
fleet_yelloweye@CurrentYr
```
<!-- slot-chunk-end -->

## OBS SLOT DESCRIPTIONS {#app:desc-obs-yelloweye}

```{r warnings = FALSE}
obs_yelloweye <- DLMtool::Precise_Unbiased
```

<!-- slot-chunk-begin -->
### Name {#app:desc-obs-name-yelloweye}

*The name of the obs_yelloweyeervation model object.*

```{r desc-obs-name-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Name
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Cobs_yelloweye {#app:desc-obs_yelloweye-cobs_yelloweye-yelloweye}

*Log-normal catch obs_yelloweyeervation error expressed as a CV. Uniform distribution lower and upper bounds.*

```{r desc-obs_yelloweye-cobs_yelloweye-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Cobs_yelloweye
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Cbiascv {#app:desc-obs-cbiascv-yelloweye}

*Log-normal CV controlling the sampling of bias in catch obs_yelloweyeervations for each simulation. Uniform distribution lower and upper bounds.*

```{r desc-obs-cbiascv-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Cbiascv
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### CAA_nsamp {#app:desc-obs-caa_nsamp-yelloweye}

*Number of catch-at-age obs_yelloweyeervation per time step. Uniform distribution lower and upper bounds.*

```{r desc-obs-caa_nsamp-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@CAA_nsamp
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### CAA_ESS {#app:desc-obs-caa_ess-yelloweye}

*Effective sample size (independent age draws) of the multinomial catch-at-age obs_yelloweyeervation error model. Uniform distribution lower and upper bounds.*

```{r desc-obs-caa_ess-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@CAA_ESS
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### CAL_nsamp {#app:desc-obs-cal_nsamp-yelloweye}

*Number of catch-at-length obs_yelloweyeervation per time step. Uniform distribution lower and upper bounds.*

```{r desc-obs-cal_nsamp-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@CAL_nsamp
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### CAL_ESS {#app:desc-obs-cal_ess-yelloweye}

*Effective sample size (independent length draws) of the multinomial catch-at-length obs_yelloweyeervation error model. Uniform distribution lower and upper bounds.*

```{r desc-obs-cal_ess-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@CAL_ESS
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Iobs_yelloweye {#app:desc-obs_yelloweye-iobs_yelloweye-yelloweye}

*Observation error in the relative abundance indices expressed as a CV. Uniform distribution lower and upper bounds.*

```{r desc-obs_yelloweye-iobs_yelloweye-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Iobs_yelloweye
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Ibiascv {#app:desc-obs-ibiascv-yelloweye}

*No longer used. Log-normal CV controlling error in obs_yelloweyeervations of relative abundance index. Uniform distribution lower and upper bounds.*

```{r desc-obs-ibiascv-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Ibiascv
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### beta {#app:desc-obs-beta-yelloweye}

*A parameter controlling hyperstability/hyperdepletion where values below 1 lead to hyperstability (an index that decreases more slowly than true abundance) and values above 1 lead to hyperdepletion (an index that decreases more rapidly than true abundance). Uniform distribution lower and upper bounds.*

```{r desc-obs-beta-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@beta
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Irefbiascv {#app:desc-obs-irefbiascv-yelloweye}

*Log-normal CV for sampling persistent bias in relative abundance index at BMSY. Uniform distribution lower and upper bounds.*

```{r desc-obs-irefbiascv-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Irefbiascv
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### Crefbiascv {#app:desc-obs-crefbiascv-yelloweye}

*Log-normal CV for sampling persistent bias in MSY. Uniform distribution lower and upper bounds.*

```{r desc-obs-crefbiascv-yelloweye, results = knitr_results, echo = knitr_echo}
obs_yelloweye@Crefbiascv
```
<!-- slot-chunk-end -->

## IMP SLOT DESCRIPTIONS {#app:desc-imp-yelloweye}

```{r warnings = FALSE}
imp_yelloweye <- DLMtool::Perfect_Imp
```

<!-- slot-chunk-begin -->
### Name {#app:desc-imp-name-yelloweye}

*The name of the Implementation error object.*

```{r desc-imp-name-yelloweye, results = knitr_results, echo = knitr_echo}
imp_yelloweye@Name
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### TACFrac {#app:desc-imp-tacfrac-yelloweye}

*Mean fraction of TAC taken. Uniform distribution lower and upper bounds.*

```{r desc-imp-tacfrac-yelloweye, results = knitr_results, echo = knitr_echo}
imp_yelloweye@TACFrac
```
<!-- slot-chunk-end -->

<!-- slot-chunk-begin -->
### TACSD {#app:desc-imp-tacsd-yelloweye}

*Log-normal CV in the fraction of TAC taken. Uniform distribution lower and upper bounds.*

```{r desc-imp-tacsd-yelloweye, results = knitr_results, echo = knitr_echo}
imp_yelloweye@TACSD
```
<!-- slot-chunk-end -->

