`r if(knitr:::is_latex_output()) '\\Appendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

# CATCH 

## Commercial Catch

Historical catch data for Inside Yellwoeye rockfish suffer from two forms of uncertainty. The first uncertainty is that commercial landings of rockfish other than Pacific Ocean Perch were reported as an aggregate (other rockfish, ORF). To reconstruct historical catches an algorithm was developed to convert ORF landings to Inside Yelloweye Rockfish landings, by fishery sector, using the ratio of Inside Yelloweye catch to ORF, from a period with credible landings data (1997-2005) from the hook and line dockside monitoring program. The ratio was then applied to the period of questionable Yelloweye catch in the reconstruction algorithm [@Haigh2011]. 

The second major source of uncertainty in historical catch timeseries is due to unreported catch that was discarded at sea. Non-retained Yelloweye Rockfish catch (releases or discards) was estimated for each fishery using the ratio of Yelloweye discarded by a fishery to fishery-specific landed targets [@Haigh2011] using data from a credible period. The catch reconstruction assumes no discarding prior to 1986 and that discards are fully reported in DFO databases since 2006.

Raw commercial catch data for Inside Yelloweye was pulled from the gfcatch database, which is maintained by the groundfish data unit at DFO. An early version of the catch reconstruction algorithm was used to develop the commercial catch time series for the previous assessment of Inside Yelloweye in 2009. However, further refinements to the reconstruction algorithm resulted in significant changes to the estimated historical catch in some years (personal comm. Norm Olsen). As well, ongoing quality control and updates to the groundfish catch database may result in minor differences in the data over time (personal comm. Maria Surry). For these reasons, the time series of commercial catch used in the current analysis differs from that used in the most recent stock assessment in 2009. 

To be consistent with the previous assessment, the total commercial catch for 1986-2005 was doubled [@DFO2012]. The original decision to double the catch for those years was based on feedback from the commercial industry and was intended to account for their lack of confidence in commercial logbooks. In the current analysis we used the reconstructed catch up to 1985 and the nominal catch from 1986 onwards. We perhaps should have used the reconstruction algorithm to obtain catches up until 2006, when full reporting and 100% monitoring was implemented in the groundfish fishery. However, sensitivity analyses demonstrated that the different catch timeseries did not affect our final perception of stock status (*cite figure Sean made*)

```{r commcatch, echo = FALSE, warning = FALSE, results = "asis"}

comm_catch <- read.csv("../data-raw/ye_catch_by_sector.csv", header=TRUE)
csasdown::csas_table(comm_catch,
                     format = "latex",
                     col_names = c("Year", "Trawl", "Halibut", "Dogfish and Lingcod", "Hook and Line Rockfish", "Total"),
                     repeat_header = TRUE,
                     caption = "Commercial catch by sector for Inside Yelloweye Rockfish.
                      The table contains reconstructed (1918-1985) and nominal (1986-2019) 
                     catch estimates in tonnes."
) %>% 
  kableExtra::column_spec(1:6, width = "1.0cm") 

```


## Recreational catch

In 2012,DFO established a coast-wide, internet-based survey of tidal water licence holders (iRec), which collects Yelloweye data. However, the results of the survey have not been calibrated to account for uncertainties such as non-response bias. Therefore the iRec data were not included in this analysis[@DFO2015].

### Reconstructed Historical Recreational Catch

Historical recreational catch, prior to 1982 was reconstructed for the previous assessment based on trends in fishing effort developed through interviews with the owners of a family run recreational fishing resort[@Yamanaka2011]. We used the same historical time series of reconstructed recreational catch for the current analysis. 

### Creel Survey Data 1982-2019

Annual catch of inside Yelloweye Rockfish by the recreational fishery is estimated by the Strait of Georgia (SOG) and the Northern Vancouver Island (NVI) creel surveys. The surveys cover Pacific Fishery Management Areas (PFMAs) 12-20, 28, and 29 [@Zetterberg2010]. Rockfish catch has been recorded in areas 13-19, 28, and 29 since 1982 but was not enumerated by species until 2000. In PFMA 12 rockfish have been counted by species since 2000 [@Zetterberg2010].

In order to estimate the catch of Yelloweye Rockfish for 1982 to 1999, the average proportion of Yelloweye to total Rockfish catch was calculated for each PFMA in 2000 and 2001. The average proportions were then used to derive estimates of Yelloweye catch from the total Rockfish catch by PFMA between 1982-1999. To estimate catch of Yelloweye in PFMA 12 for the years 1982-1999, the average proportion of Yelloweye in total Rockfish catch over 2000 and 2001 was calculated and applied to the total Rockfish catch for the rest of the SOG in each year. To be consistent with the previous assessment, an adjustment of 1.09 was applied to total annual effort to account for lack of records in PFMA 12, where effort was not recorded prior to 2000. We converted rockfish pieces to weight by multiplying by 2.49kg, which was the average weight of Yelloweye sampled in the creel surveys between 2000 and 2008. 

```{r reccatch, echo=FALSE, warning=FALSE, results="asis"}


rec_catch <- read.csv("../data-raw/rec-allcatch-effort.csv", header=TRUE) 

# make a table of recreational catch
csasdown::csas_table(rec_catch,
                     format = "latex",
                     col_names = c("Year", "Catch(t)", "Effort(boat trips)"),
                     align=c("c","c","c"),
                     digits=1,
                     repeat_header = TRUE,
                     caption = "Recreational catch estimates for inside Yelloweye Rockfish.
                      The table contains reconstructed (1918-1981) and modern (1982-2019) 
                     catch estimates in tonnes."
) 
```

\clearpage
```{r recbyarea, echo=FALSE, warning=FALSE, results = "asis"}

rec_area <- read.csv("../data-raw/rec-catcheffortbyarea.csv", header=TRUE)

# organizing the data from long to wide format

rec_wide <- rec_area %>% 
  select(year, tonnes, totaleffort, pfma) %>% 
  pivot_wider(names_from = pfma, values_from = c(tonnes, totaleffort)) %>% 
  mutate(effort = rowSums(.[13:23], na.rm=TRUE)/10000) %>% 
  select(-starts_with("totaleffort")) %>% 
  rename_at(vars(starts_with("tonnes_")), funs(str_remove(., "tonnes_")))

# make the table of catch by PFMA and total effort by year
csasdown::csas_table(rec_wide,
                     format = "latex",
                     digits=1,
                     caption = "Estimated yelloweye rockfish (Sebastes ruberrimus) recreational catch in tonnes from the inside Strait of Georgia creel survey by statistical area (PFMA) and total effort in 10,000 boat trips by year from 1982 to 2019.Numbers of fish were converted to weight using 2.49 kg (average weight of yelloweye rockfish in the creel survey 2000-2008)."
) %>% 
  kableExtra::column_spec(1:13, width = "0.75cm") 
  
```

## Food, Social, and Ceremonial (FSC) Catch

What did they do in the previous assessment and why was it no good? e.g. consumption rates which was not supported by conversations with indigenous reps.

The data in *table XX* was collected from dual fishing trips by the commercial dockside monitoring program. Dual fishing trips ocurr when indigenous fishers choose to keep some of the catch obtained during a commercial fishing trip for FSC purposes. The table shows the proportion of the catch from each dual fishing trip that was taken for FSC. These proportions are incorporated into the annual totals for commercial catch within the groudfish sector databases. Therefore, a separate analysis to construct a timeseries of FSC catch was not undertaken in this evaluation. 

The data is collected at the trip level, not set level, therefore there may be issues with some of the reported catch being collected outside the geographic boundary for Inside Yelloweye. 


```{r fsc-catch, echo=FALSE, results = "asis"}

fsc_catch <- read.csv("../data-raw/fsc-dmp.csv", header=TRUE)

csasdown::csas_table(fsc_catch, 
                     format = "latex",
                     col_names = c("Year", "FSC", "Commercial", "Total", "Percent FSC"),
                     caption = "FSC catch of Inside Yelloweye Rockfish as a proportion of total commercial catch reported to dockside observers from dual fishing trips." )

```
