# CATCH DATA {#app:catch-data}

Inside Yelloweye Rockfish is targeted in hook and line commercial fisheries, Food Social and Ceremonial (FSC) fisheries, and recreational fisheries.

## COMMERCIAL CATCH DATA {#sec:com-catch-data}

*TODO: please provide the years for which the reconstruction was done ---- 1918-2005, but we only used the reconstruction from 1918 to 1985. The "credible period" of data used in the reconstruction is from 1997-2005. see explanation in paragraph 1. They ended in 2005 because that was the last year of data in one of the databases they were using -- MJB--* 

Rockfish catch data can be grouped into 3 time periods: historic (1918-1950), early electronic (1951-2005), and modern (2006 onwards). There are two major sources of uncertainty in the historical and early electronic periods for Inside Yelloweye rockfish. The first uncertainty is that rockfish catch, other than Pacific Ocean Perch, was reported as an aggregate (other rockfish, ORF) in historical landings. To reconstruct historical catches an algorithm was developed by Rowan Haigh and Lynn Yamanaka of DFO [@haigh2011]. The reconstruction algorithm applies a ratio calculated from a period with credible landings data from the hook and line dockside monitoring program (1997-2005) and applies it to generate a time series of catch by species, year, fishery sector, and management area [@haigh2011]. "Credible" landings data are taken from reference years where catch knowledge was considered high and stable, beginning in the 1997 with the start of observer trawl coverage and the individual vessel quota system [@haigh2011]. 

The second major source of uncertainty is the magnitude of unreported catch that was released or discarded at sea, prior to the introduction of 100% observer coverage in 2006. The catch reconstruction of @haigh2011 assumes no discarding prior to 1986, when the ZN licence was instituted. Prior to that it is assumed all Rockfish were kept. Discards are assumed to be fully reported in DFO databases since 2006 and the introduction of 100% observer coverage. Non-retained Yelloweye Rockfish catch (releases or discards) was estimated for each fishery using the ratio of Yelloweye discarded by a fishery to fishery-specific landed targets using data from 2000-2004 hook and line observer logs. The estimated historical unreported catch was then incorporated into the catch reconstruction, giving a final annual total.  

The commercial catch time series used in this analysis differs from the one previously reported in 2009, for several reasons. Ongoing quality control and updates to the groundfish catch database may result in minor differences in the data over time (Maria Surry, DFO, Pacific Biological Station, pers. comm., March 9, 2020 ). As well, an earlier version of the catch reconstruction algorithm was used to develop the catch time series for the previous stock assessment by @yamanaka2011, as the final version had not yet been published. Further refinements to the reconstruction algorithm resulted in significant changes to the estimated historical catch in some years (Norm Olsen, DFO, Pacific Biological Station, pers. comm., March 9,2020 ).

The reconstruction algorithm could have been applied to all years in the timeseries until to 2005 (after which full at-sea and dockside monitoring came into effect). However, for this analysis we used the reconstructed catch data from 1918-1985, switching to the nominal catch data in 1986. The nominal catch from 1986-2005 was then doubled to calibrate our OMs,to be consistent with the previous assessment [@yamanaka2011]. In 2009, advice from industry representatives indicated that the scale of unreported catch was probably equal to landed catch (hence the doubling of the nominal catch). Because discards are estimated as part of the catch reconstruction we did not use the reconstructed catch for the period 1986-2004, to avoid double counting of discards or misreported catch.

*TODO: double check this was just about discards and not discards + misreporting*

*TODO: Sean made a figure proving that it didn't make much difference. Maybe include it here?*
 
In the current analysis we explore one OM scenario where the 1986-2005 commercial catches were not doubled ("Low catch" scenario, Section \ref(sec:approach3-reference2)).

*TODO: We used doubled commercial catches from 1986 to 2005 so these should be reflected in this table. Only the Low catch scenario used nominal catch from 1986-2005 *


\clearpage

```{r commcatch, echo = FALSE, warning = FALSE, results = "asis"}
comm_catch <- read.csv(here("data-raw/ye_catch_by_sector.csv"))
csasdown::csas_table(comm_catch,
  format = "latex",
  col_names = c("Year", "Trawl", "Halibut", "Dogfish and Lingcod", "Hook and Line Rockfish", "Total"),
  repeat_header = TRUE,
  caption = "Commercial catch by sector for Inside Yelloweye Rockfish. The table contains reconstructed (1918-1985) and nominal (1986-2019) catch estimates in tonnes. *Nominal catch shown here was doubled for all OMs except the low catch scenario."
) %>%
  kableExtra::column_spec(1, width = "1.0cm") %>%
  kableExtra::column_spec(2:6, width = "1.6cm") 
```


```{r commcatch2, out.width="\\textwidth", fig.width=6, fig.cap="Commercial catch by sector for Inside Yelloweye Rockfish. This figure contains reconstructed (1918--1985) and nominal (1986--2019) catch estimates in tonnes. Note that, although nominal catch for 1986--2005 was doubled in all OMs except the low catch scenario, we do not show the doubled catch in this figure."}
tidyr::pivot_longer(comm_catch, -1) %>%
  dplyr::filter(name != "Total t") %>% 
  ggplot(aes(year, value, fill = name)) + geom_col(width = 1) +
  gfdlm::theme_pbs() +
  scale_fill_brewer(palette = "Set2") + 
  coord_cartesian(expand = FALSE) +
  labs(fill = "Sector", y = "Catch (t)") +
  theme(axis.title.x = element_blank(), legend.position = "bottom",
    plot.margin = margin(t = 11 / 2, r = 11 / 2 + 5, b = 11 / 2, l = 11 / 2)
)
```



\clearpage

## RECREATIONAL CATCH DATA {#sec:rec-catch-data}

In 2012, DFO established a coast-wide, internet-based survey of tidal water licence holders (iRec), which collects Yelloweye data. However, the results of the survey have not been calibrated to account for uncertainties such as non-response bias. Therefore the iRec data were not included in this analysis[@dfo2015].

### Reconstructed Historical Recreational Catch {#sec:recon-rec-catch-data}

Historical recreational catch, prior to 1982 was reconstructed for the previous assessment based on trends in fishing effort developed through interviews with the owners of a family run recreational fishing resort[@yamanaka2011]. We used the same historical time series of reconstructed recreational catch for the current analysis.

### Creel Survey Data 1982-2019 {#sec:creel-catch-data}

Annual catch of inside Yelloweye Rockfish by the recreational fishery is estimated by the Strait of Georgia (SOG) and the Northern Vancouver Island (NVI) creel surveys. The surveys cover Pacific Fishery Management Areas (PFMAs) 12-20, 28, and 29 [@zetterberg2010]. Rockfish catch has been recorded in areas 13-19, 28, and 29 since 1982 but was not enumerated by species until 2000. In PFMA 12 rockfish have been counted by species since 2000 [@zetterberg2010].

We followed the same method as in Yamanaka et al. (2011) to estimate the catch of Yelloweye Rockfish for 1982 to 1999, the average proportion of Yelloweye to total Rockfish catch was calculated for each PFMA in 2000 and 2001. The average proportions were then used to derive estimates of Yelloweye catch from the total Rockfish catch by PFMA between 1982-1999. To estimate catch of Yelloweye in PFMA 12 for the years 1982-1999, the average proportion of Yelloweye in total Rockfish catch over 2000 and 2001 was calculated and applied to the total Rockfish catch for the rest of the SOG in each year. To be consistent with the previous assessment, an adjustment of 1.09 was applied to total annual effort to account for lack of records in PFMA 12, where effort was not recorded prior to 2000. We converted rockfish pieces to weight by multiplying by 2.49kg, which was the average weight of Yelloweye sampled in the creel surveys between 2000 and 2008.

\clearpage

```{r reccatch, echo=FALSE, warning=FALSE, results="asis"}
library(tidyverse)
rec_catch <- read.csv(here("data-raw/rec-allcatch-effort.csv"))
rec_catch %>% mutate_if(is.numeric, replace_na, replace = "--")
# make a table of recreational catch
csasdown::csas_table(rec_catch,
  format = "latex",
  col_names = c("Year", "Catch (t)", "Effort (boat trips)"),
  align = c("c", "c", "c"),
  digits = 1,
  repeat_header = TRUE,
  caption = "Recreational catch estimates for inside Yelloweye Rockfish. The table contains reconstructed (1918-1981) and modern (1982-2019) creel survey catch estimates in tonnes."
)
```

```{r reccatch2, out.width="\\textwidth", fig.width=6, fig.cap="Recreational catch estimates for Inside Yelloweye Rockfish. The figure shows reconstructed (1918-2019) and modern creel survey (1982-2019) catch estimates in tonnes."}
tidyr::pivot_longer(rec_catch, -1) %>%
  mutate(name = gfutilities::firstup(gsub("_", " ", name))) %>%
  mutate(name = gsub("Hook line rockfish", "Hook and line rockfish", name)) %>%
  mutate(name = gsub("Dogfish lingcod", "Dogfish and lingcod", name)) %>%
  dplyr::filter(name != "Total t") %>% 
  ggplot(aes(year, value, fill = name)) + geom_col(width = 1) +
  gfdlm::theme_pbs() +
  scale_fill_brewer(palette = "Set2") + 
  coord_cartesian(expand = FALSE) +
  labs(fill = "Sector", y = "Catch (t)") +
  theme(axis.title.x = element_blank(), legend.position = "bottom",
    plot.margin = margin(t = 11 / 2, r = 11 / 2 + 5, b = 11 / 2, l = 11 / 2)
)
```

\clearpage

```{r recbyarea, echo=FALSE, warning=FALSE, results = "asis"}
rec_area <- read.csv(here("data-raw/rec-catcheffortbyarea.csv"))

# organizing the data from long to wide format
rec_wide <- rec_area %>%
  select(year, tonnes, totaleffort, pfma) %>%
  tidyr::pivot_wider(names_from = pfma, values_from = c(tonnes, totaleffort)) %>%
  mutate(effort = rowSums(.[13:23], na.rm = TRUE) / 10000) %>%
  select(-starts_with("totaleffort")) %>%
  rename_at(vars(starts_with("tonnes_")), list(~ stringr::str_remove(., "tonnes_")))

# make the table of catch by PFMA and total effort by year
csasdown::csas_table(rec_wide,
  format = "latex",
  digits = 1,
  caption = "Estimated yelloweye rockfish (Sebastes ruberrimus) recreational catch in tonnes from the inside Strait of Georgia creel survey by statistical area (PFMA) and total effort in 10,000 boat trips by year from 1982 to 2019.Numbers of fish were converted to weight using 2.49 kg (average weight of yelloweye rockfish in the creel survey 2000-2008)."
) %>%
  kableExtra::column_spec(1:13, width = "0.75cm")
```

\clearpage

## FOOD, SOCIAL, AND CEREMONIAL CATCH (FSC) {#sec:fsc-catch-data}

Yelloweye Rockfish are an important traditional food source of coastal First Nations in BC [@eckert2018], including in the inside waters of 4B. Total FSC catch data of Yelloweye Rockfish, as well as other groundfish species, are not available for either the historic or contemporary time period and particularly not available resolved to the species [M. Fetterly and A. Rushton, pers. comm.].
To account for FSC catch in the last stock assessment, Yamanaka et al. (2011) used a consumption rate (0.23 kg/year/person), which was half of the consumption rate determined in a traditional diet study from Southeast Alaska, applied to the First Nations population near area 4B over the time series (1918-2009).
This approach assumes that the consumption rate of Yelloweye Rockfish by First Nations has remained constant through time, despite the fact that European colonization is known to have impacted most aspects of Indigenous society over this same time period.
A decline in the amount of fish and seafood consumed by First Nations in BC has been attributed to numerous social, ecological, and economic factors including the loss of traditional territories, diminished traditional knowledge transmission, and barriers such as poverty that makes buying boats and fishing gear unattainable for many communities -->[add ref-@marushka2019]<--.
Specific to the southern part of our study area, the Coast Salish people have seen their relationship to marine resources eroded due to the development of commercial and recreational fisheries, as well as policy and political decisions -->[add ref-@ayers2012]<--.
We did not, therefore, follow the methods used in Yamanaka et al. (2011).

The only FSC data that are available are from the commercial dockside monitoring program (DMP) between 2006 and 2019 *table XX*. These data were collected from "dual fishing" trips which occur when indigenous fishers choose to keep some of the catch obtained during a commercial fishing trip for FSC purposes.
Both commercial and FSC catch are monitored during the offload.
Between 0 and 0.8 T amounting to and average of 5.6% of the total commercial catch has been landed on dual fishing trips in this time period.
The FSC catch from these dual trips is included in the annual totals for commercial catch within the groundfish sector databases.
The data are, however, collected at the trip level, not set level, therefore some of the reported catch might be from outside of Area 4B.
Dual fishing trips that could not be mostly attributed to 4B or outside waters were excluded from this analysis.
Most of the dual fishing trips from the northern part of the study area because this is also where most of the commercial fishing for Yelloweye Rockfish in 4B currently occurs.
Indigenous fishers from the member First Nations represented by the A-Tlegay Fisheries Society, are largely obtaining Yelloweye Rockfish on dual fishing trips (Christa Rusel, pers. comm.).

In the southern part of the study area, indigenous fishers have little commercial capacity
FSC catch in the Strait of Georgia is, therefore, primarily from small recreational boats (C. Ayers, pers. comm.).
Similar to how some of the FSC catch is accounted with the commercial catch data, the FSC effort from small boats will be captured in the recreational data from the creel survey program.
Although FSC fishers are not constrained by recreational catch limits or closures, their boats will be counted on the aerial portion of the creel survey, and therefore contribute to the expanded recreational catch estimates.
The proportion of FSC fisher encountered by the dockside creel monitor was not, however, readily available in the recreational database (CREST) (P. Zetterberg, pers. comm.).

\clearpage

```{r fsc-catch, echo=FALSE, results = "asis"}
fsc_catch <- read.csv(here("data-raw/fsc-dmp.csv"))
csasdown::csas_table(fsc_catch,
  format = "latex",
  col_names = c("Year", "FSC", "Commercial", "Total", "Percent FSC"),
  caption = "FSC catch of Inside Yelloweye Rockfish as a proportion of total commercial catch reported to dockside observers from dual fishing trips."
)
```

\clearpage

## CHRONOLOGY OF MANAGEMENT CHANGES

```{r, echo=FALSE, warning=FALSE, results="asis"}
timeline <- readr::read_csv(here("data-raw/management-chronology.csv"))

csasdown::csas_table(timeline,
  format = "latex",
  col.names = c("Year", "Area", "Management Action"),
  caption = "History of management changes for the directed hook and line Yelloweye Rockfish (*Sebastes ruberrimus*) fishery from 1986 to 2019."
) %>%
  kableExtra::column_spec(1, width = "2.5cm") %>%
  kableExtra::column_spec(2, width = "1.75cm") %>%
  kableExtra::column_spec(3, width = "7.5cm")
```
