# HBLL INSIDE SURVEY INDEX

```{r}
include_hbll_fig <- function(file) {
  knitr::include_graphics(here::here("figs", file), dpi = NA)
}
```

```{r, fig.cap="The raw data. Gray background shading indicates the northern and southern survey areas. The area of the circles represents the number of fish caught per hook after accounting for hook competition."}
include_hbll_fig("hbll-joint-raw-data.pdf")
```

```{r, out.width="4in", fig.cap="Stochastic Partial Differential Equation (SPDE) mesh from INLA. 400 knots. kmeans clustering algorithm. Samples from all years are shown simultaneously."}
include_hbll_fig("hbll-joint-spde.pdf")
```

```{r, out.width="5in", fig.cap="Area per survey grid cell."}
include_hbll_fig("hbll-area-in-water.pdf")
```

```{r, fig.cap="Baited hooks. Note the substantial difference between the northern and southern areas and the change in the north between 2003--2007 in subsequent years."}
include_hbll_fig("hbll-joint-baited.pdf")
```

```{r, fig.cap="Hook adjustment factor."}
include_hbll_fig("hbll-joint-hook-adjust.pdf")
```

```{r, fig.cap="Predicted relative density in space and time."}
include_hbll_fig("hbll-joint-prediction-log.pdf")
```

```{r, fig.cap="The spatial random effects. These are consistent differences from the expectation in space.", out.width="4in"}
include_hbll_fig("hbll-joint-omega.pdf")
```

```{r, fig.cap="The spatiotemporal random effects. Note the reversion to the mean in area-year combinations without sampling data. Also note the difference in magnitude between the spatiotemporal and spatial random effects."}
include_hbll_fig("hbll-joint-epsilon.pdf")
```

```{r, fig.cap="Randomized quantile residuals from the model shown in space and time."}
include_hbll_fig("hbll-joint-residual-map.pdf")
```

```{r, out.width="4in", fig.cap="The joint relative abundance index. Top panel shows the joint prediction from the spatial temporal model. Included are three versions: (1) random effects and annual means only, (2) adding a depth covariate, and (3) removing the hook adjustment factor. The middle and bottom panels show the joint predictions for the northern and southern areas. All shaded regions represent 95\\% confidence intervals. The joint index timeseries in the top panel have been scaled to have the same geometric mean as the main ``HBLL INS'' index for visualization purposes. In the second and third rows, the solid dots represent years with observations and the open dots represent years without observations. Similarly, the dashed vertical lines indicate years with surveys (mostly) in the southern area."}
include_hbll_fig("hbll-index-components-eps-depth2.pdf")
```


# DOGFISH SURVEY

Notes:

I'm estimating the index for an "average" hook type. If we estimate for one or the other type then it puts more or less uncertainty into the first or second half of the time series (the estimates themselves are just scaled though).

It is now able to estimate spatiotemporal random effects and with the help of the spatial correlation it seems to be better able to estimate the hook type correction with appropriate uncertainty. You can see the estimated correction factor in the model output:

exp(2.04)
[1] 7.690609

exp(2.04 + c(-2, 2) * 0.80)
[1]  1.552707 38.091837

I'm sure thats an exaggeration, but so it is with few data points and no priors. At least by including it in one model we can let the data speak for themselves.

I am creating the index on the rectangles that define the dogfish survey. I overlaid a 500m x 500m grid on the dogfish survey rectangles and am now also removing any of those fine scale grid cells that overlap land.

```{r, fig.cap="SPDE", out.width="4in"}
include_hbll_fig("dogfish-joint-spde.png")
```

```{r, fig.cap="Raw data"}
include_hbll_fig("dogfish-yelloweye-per-area-data.png")
```

```{r, fig.cap="Spatial residuals with some jittering."}
include_hbll_fig("dogfish-residual-map.png")
```

```{r, fig.cap="Prediction with log transformed color scale."}
include_hbll_fig("dogfish-prediction-log.png")
```

```{r, fig.cap="Spatial random effects.", out.width="4in"}
include_hbll_fig("dogfish-omega.png")
```

```{r, fig.cap="Spatiotemporal random effects."}
include_hbll_fig("dogfish-epsilon.png")
```

```{r, fig.cap="Standardized index.", out.width="4in"}
include_hbll_fig("dogfish-index-estimated-hook.png")
```

\clearpage

Model:

```
Spatiotemporal model fit by REML ['sdmTMB']
Formula: ye_count ~ 0 + circle_hook_centered + as.factor(year) + log(dogfish_count) + 
Formula:     offset
SPDE: sp
Family: nbinom2(link = 'log')
                     coef.est coef.se
circle_hook_centered     2.04    0.80
as.factor(year)1986      1.48    1.20
as.factor(year)1989      1.83    1.25
as.factor(year)2004      0.08    1.09
as.factor(year)2005     -0.20    1.19
as.factor(year)2008     -0.07    1.13
as.factor(year)2011     -0.27    1.19
as.factor(year)2014     -0.31    1.11
as.factor(year)2019      0.75    1.11
log(dogfish_count)      -0.31    0.14

Matern range parameter: 0.36
Dispersion parameter: 0.32
Spatial SD (sigma_O): 1.80
Spatiotemporal SD (sigma_E): 0.77
REML criterion at convergence: 428.921
```
